\vspace{-1cm}\Large{\textsf{The Size Distribution of Firms and Industrial Water Pollution: A Quantitative Analysis of China} \\ \textsf{Replication Instruction}}

### 2019-09-18 Documentation/Replication_Instruction.tex
replication done

% Functional Package
\usepackage{enumerate}
\usepackage{url}      % This package helps to typeset urls

@@

This note explains step-by-step how to replicate all the results in \textit{The Size Distribution of Firms and Industrial Water Pollution: A Quantitative Analysis of China}. We begin with several house-keeping notes. We begin with some housekeeping stuff in Section \rom{1}. Section \rom{2} explains in detail how to replicate all the empirical results.

\section{Housekeeping Stuff}

To replicate all the results in the paper, three softwares are used. Specifically, \textsc{Stata} is used for initial data processing. All the empirical results are then produced using \code{R}. We use MATLAB to compute all the quantitative results. There is no particular scientific reason that we use one statistical software (\textsc{Stata}) for data cleaning and the other (\code{R}) for empirical analysis. It is easier to handle Chinese characters with \textsc{Stata} while \code{R} switches back and forth between different datasets swiftly. Veterans of \textsc{Stata} (or \code{R}) should be able to replicate all the empirical results with just one software using our source code as reference with ease. In addition, which in fact should go without saying, for readers without a licence to MATALB, GNU Octave could be used instead.

We use three datasets in our analysis: The National General Survey of Pollution Sources (NGSPS, \begin{CJK}{GBK}{kai}第一次全国污染源普查\end{CJK}), The National Economic Census (CNEC, \begin{CJK}{GBK}{kai}第一次全国经济普查\end{CJK}) and the Statistics of U.S. Businesses (SUSB).
\begin{itemize}
    \item
    The NGSPS is a confidential dataset housed at the Ministry of Ecology and Environment. The data can only be accessed within the Ministry of Ecology and Environment as well as institutions under its direct supervision. Individual researchers requesting access should submit the application through the official portal for Information Access (\begin{CJK}{GBK}{kai}政府信息公开\end{CJK}) by the Ministry of Ecology and Environment at the following url: \url{http://www.mee.gov.cn/weihu/201706/t20170625_416641.shtml}. The url is retrieved on September 15th, 2019 and may vary in the future. All applications are subject to official approval by the Ministry of Ecology and Environment.
    \item
    The CNEC is also a confidential dataset belonging to National Bureau of Statistics of China. Many universities and institutions have legal copy of the dataset. Our copy was obtained from Wuhan University. One portal to request access to the data for individual researchers is through the Micro-data Lab of the National Bureau of Statistics (\begin{CJK}{GBK}{kai}国家统计局微观数据实验室，国家统计局-清华大学数据开发中心\end{CJK}). The url, retrieved on September 15th, 2019, is \url{http://microdata.stats.gov.cn/}; and again it may vary in the future. All applications are subject to official approval by the National Bureau of Statistics.
    \item
    The SUSB is publicly available from the Census Bureau's dedicated website. The url, retrieved on September 15th, 2019, and subject to possible change in the future, is \url{https://www.census.gov/programs-surveys/susb.html}.
\end{itemize}

In the replication files, we cannot provide micro-level data of the NGSPS, due to the Non-Disclosure Agreement with the Ministry of Ecology and Environment. Therefore, we only post the source code that generates the results. The NGSPS is used to compute the following results:
\begin{itemize}
    \item
    Tables: 1, 2, A.1, C.1, D.1 and F.1.
    \item
    Figures: 1, B.1 (upper panels), C.1, C.2, D.3.
    \item
    Regressions: 1 and the un-numbered one in Section \rom{1}.B, 2, 3, the 6 un-numbered regression in Appendix C.1 and the un-numbered regression in Appendix D.2.
    \item
    Some miscellaneous information scattered across the paper.
\end{itemize}

\section{Empirical Results}

The instructions are organized by logic instead of the order of appearance in the paper.

\section{Quantitative Results}

>>>>

% Functional Package
\usepackage{enumerate, enumitem}
\usepackage{url}      % This package helps to typeset urls

@@

This note explains step-by-step how to replicate all the results in \textit{The Size Distribution of Firms and Industrial Water Pollution: A Quantitative Analysis of China}. We begin with some housekeeping stuff in Section \rom{1}. Section \rom{2} explains in detail how to replicate all the results in the main text. Section \rom{3} shows how the results in the appendices can be replicated.

\section{Housekeeping Information}

\subsection{Overview}

To replicate all the results in the paper, three softwares are used. Specifically, \textsc{Stata} is used for initial data processing. All the empirical results are then produced using \code{R}. MATLAB is used to compute all the quantitative results. There is no particular scientific reason that we use one statistical software (\textsc{Stata}) for data cleaning and the other (\code{R}) for empirical analysis.\footnote{Due to limited backward compatibility of \textsc{Stata} and that the \code{foreign} package of \code{R} supports only \code{.dta} files saved by \textsc{Stata} up to Version 12, to run the code without any modification, the reader would need \textsc{Stata} 12. Readers with more recent version of the \textsc{Stata} would need to either modify in the \code{.do} file everywhere \code{.dta} files are read and written, or use alternative \code{R} package (for instance \code{readstata13}) to convert the data in \bcode{cpsc\_convert.R} and \bcode{cec\_convert.R}. Compatibility of our code is not tested under such environments. However, none of our results should be affected though.} We do this simply because it is easier to handle Chinese characters with \textsc{Stata} while \code{R} switches back and forth between different datasets swiftly. Veterans of \textsc{Stata} (or \code{R}) should be able to replicate all the empirical results with just one software using our source code as reference with ease. In addition, which in fact should go without saying, for readers without a licence to MATALB, GNU Octave could be used instead.

We use three datasets in our analysis: The National General Survey of Pollution Sources (NGSPS, \begin{CJK}{GBK}{kai}第一次全国污染源普查\end{CJK}), The National Economic Census (CNEC, \begin{CJK}{GBK}{kai}第一次全国经济普查\end{CJK}) and the Statistics of U.S. Businesses (SUSB).
\begin{itemize}
    \item
    The NGSPS is a confidential dataset housed at the Ministry of Ecology and Environment (MEE henceforth). The dataset is subject to regulation by \textit{The Law of the People's Republic of China on Guarding State Secrets} \begin{CJK}{GBK}{kai}（中华人民共和国保守国家秘密法）\end{CJK} because it contains sensitive information. Please refer to \textit{Regulation on Archiving the National General Survey of Pollution Sources Data (State Environmental Protection Administration [2007] No.187)} {\begin{CJK}{GBK}{kai}（污染源普查档案管理办法[环发[2007]187号]）\end{CJK}}. The data can only be accessed within the MEE as well as institutions under its direct supervision \begin{CJK}{GBK}{kai}（中华人民共和国生态环境部及其直属单位）\end{CJK}. Researchers affiliated with these institutions should submit application for access following the internal procedure of the MEE. This is how we access the data.

    Individual researchers not affiliated with the MEE and institutions under its direct supervision needs to submit the application through the official portal for Information Access (\begin{CJK}{GBK}{kai} 政府信息公开\end{CJK}) by the MEE at the following url: \url{http://www.mee.gov.cn/weihu/201706/t20170625_416641.shtml}. The url is retrieved on September 15th, 2019 and may vary in the future. All applications are subject to official approval by the General Office of Ministry of Ecology and Environment \begin{CJK}{GBK}{kai}（中华人民共和国生态环境部办公厅）\end{CJK}.

    For an official introduction to the NGSPS and declassified information at the aggregated level, interested readers could refer to the book \textit{Data Collection of the National General Survey of Pollution Sources} \begin{CJK}{GBK}{kai}（《污染源普查数据集》，中国环境科学出版社，2011）\end{CJK}, which is publicly available.
    \item
    The CNEC is also a confidential dataset belonging to National Bureau of Statistics of China. Many universities and institutions have legal copy of the dataset though. Our copy was obtained from Fudan University.
    \item
    The SUSB is publicly available from the Census Bureau's dedicated website. The url, retrieved on September 15th, 2019, and subject to possible change in the future, is \url{https://www.census.gov/programs-surveys/susb.html}.
\end{itemize}

In the replication files, we cannot provide micro-level data of the NGSPS and CNEC, due to non-disclosure agreements with the MEE and Fudan University. Therefore, we only post the source code that generates the results. However, to facilitate replication by the readers who have access to the datasets, we post the log files when running the analysis on our computer.

\subsection{File Structures}

The readers will get a number of files for replicating the results. To ease digestion, we briefly introduce the structure of the folders and files. As typographical convention, we use \bcode{blue computer modern typewriter} to indicate \bcode{folders} and \bcode{files}. The current folder is referred to as \bcode{./}.
\begin{itemize}
    \item
    \bcode{./Empirical/}:
    \begin{itemize}
        \item
        \bcode{./Data/}: contains the raw and cleaned data.
        \item
        \bcode{./Results/}: contains all the figures and log-files.
        \item
        \bcode{./cpsc\_raw.do}: does initial processing of the NGSPS.
        \item
        \bcode{./cec\_clean.do}: does initial processing of the CNEC.
        \item
        \bcode{./cpsc\_convert.R}: converts the NGSPS to binary format of \code{R}.
        \item
        \bcode{./cec\_convert.R}: converts the CNEC to binary format of \code{R}.
        \item
        \bcode{./Empirical\_AEJ.R}: produces most empirical results in the main text.
        \item
        \bcode{./Empirical\_Appendix.R} produces most empirical results in the appendices.
        \item
        \bcode{./Accounting.R}: executes the accounting exercise.
        \item
        \bcode{./Descriptive.R}: computes some summary statistics of the NGSPS.
    \end{itemize}
    \item
    \bcode{./Quantitative/}
    \begin{itemize}
        \item
        \bcode{./Results/}: contains all the results and figures.
        \item
        \bcode{./twosectors.m}: computes the equilibrium of the two-sector model with perfect substitution used in the main text and saves the results in \bcode{.mat} format.
        \item
        \bcode{./fcn2.m}: computes the excess demand at a given vector of price; called by \bcode{twosectors.m}.
        \item
        \bcode{./compute\_tables.m}: computes the raw data used to calculate Tables 4, 5 and 6 in the main text.
        \item
        \bcode{./plot\_figures.m}: plots Figures 4 and 5 in the main text.
        \item
        \bcode{./twosectors\_ces.m}: computes the equilibrium of the two-sector model with constant elasticity of substitution used in Appendix J and saves the results in \bcode{.mat} format.
        \item
        \bcode{./fcnces.m}: computes the excess demand at a given vector of price; called by \\
        \bcode{twosectors\_ces.m}.
        \item
        \bcode{./compute\_tables\_ces.m}: computes the raw data used to calculate Tables J.1 in Appendix J.
        \item
        \bcode{./misc.m}: draws Figure D.2 and computes the decomposition in Sections \rom{4}.A and \rom{4}.B of the main text.
    \end{itemize}
\end{itemize}

All the file reference in the source code is specified by relative position. Please set the working director of your software to the current folder that hosts the file. For example, if the package is saved locally at \bcode{C:/Users/AEJ/pollution\_rep/}, then to replicate the empirical results, the working directory of \textsc{Stata} and \code{R} should all be set to \bcode{C:/Users/AEJ/pollution\_rep/Empirical}, while the MATLAB working directory should be set to \bcode{C:/Users/AEJ/pollution\_rep/Quantitative} when replicating the quantitative results.

\subsection{Data Cleaning}

The NGSPS comes by 5 \textsc{Stata} \code{.dta} files. \bcode{keynum.dta} contains information of the key sources, while \bcode{reg1.dta} to \bcode{reg4.dta} host information of the regular sources. There are 4 files for the regular sources because of the technical limitation back when we initially applied for the data. It is likely that the reader will get one file for the regular source at this moment. These files should be placed under \bcode{./Empirical/Data/}. Executing \bcode{cpsc\_raw.do} will combine the four \bcode{regx.dta} to \bcode{regall.dta} and label all the variables in \bcode{keynum.dta} and \bcode{regall.dta}. It also generates another file \bcode{allfirms.dta} where the two files are combined. All three files are saved under \bcode{./Empirical/Data/}.

Our copy of the CNEC has two \textsc{Stata} \code{.dta} files. \bcode{cec2004\_large\_full.dta} holds those samples that overlap with the commonly used 2004 Annual Surveys of Industrial Firms, while \bcode{cec2004\_small.dta} contains small firms not surveyed in the annual ASIF. Again, they should be placed under \bcode{./Empirical/Data/}. The file \bcode{cec\_clean.do} labels all the variables. Upon completion, the original un-labeled files will be replaced by files of the same name.

With these two steps completed, the reader needs to convert the data from \textsc{Stata} \code{.dta} to the internal binary \code{R} format \code{.RData}. File \bcode{cpsc\_convert.R} converts \bcode{keynum.dta} to \bcode{KEYFIRM\_R.RData}, \bcode{regall.dta} to \bcode{REGFIRM\_R.RData} and \bcode{allfirms.dta} to \bcode{ALLFIRM\_R.RData}. Similarly, \bcode{cec\_convert.R} converts \\ \bcode{cec2004\_small.dta} to \bcode{DSMALL\_R.RData}, \bcode{cec2004\_large\_full.dta} to \bcode{DLARGE\_R.RData}. It then extracts only the variables used in the paper and combines the two \code{.RData} files to one file \bcode{CNEC\_avgp.RData}. All the files are saved under \bcode{./Empirical/Data/} as before.

The SUSB data are directly downloaded from the Census website as \bcode{susb04.csv}. We use the dataset in its original form.

In what follows, we will only be using the files converted by \code{R}. A list of the essential files is provided below. All the files should be placed under \bcode{./Empirical/Data/}. For ease of reference, we use the two-letter acronyms in parenthesis when referring to the data files later.
\begin{itemize}
    \item
    \bcode{KEYFIRM\_R.RData (PK)}: Key sources of the NGSPS.
    \item
    \bcode{ALLFIRM\_R.RData (PA)}: All sources of the NGSPS.
    \item
    \bcode{CNEC\_avgp.RData (CA)}: All samples in the CNEC.
    \item
    \bcode{DLARGE\_R.RData (DL)}: A subset of \code{CA} which overlaps with the 2004 Annual Surveys of Industrial Firm.    
    \item
    \bcode{susb04.csv (US)}: SUSB 2004.
\end{itemize}

\section{Replicate Results in the Main Text}

We try to organize our source code by sections in the paper as much as we can. This is not always possible though (or creates unnecessary confusion). We do, however, break the code by sections within the file, where tasks that are reasonably connected logically are grouped together. The code is written such that each section is self-contained, so the readers do not have to run from the very beginning if she/he only wants to replicate a certain result. Table \ref{tab:navi_main} summarizes the correspondence between the results in the paper (tables, figures, regression results, in-text numbers, etc.) and the section of code files that computes them, as well as data dependency. To further assist the readers to visually navigate through the code, important sections are always indicated by a 76-character line of \code{=}. This is the longest line in all the source code, and should be those most visually noticeable amongst all.

We now explain how to replicate the results in the main text step-by-step. The results are presented in the order of appearance in the main text.

\begin{table}[t]
\footnotesize
\centering
\begin{threeparttable}
\caption{Navigating the Main Text}
\begin{tabular}{llll}
    \hline \hline
    Content                         & File Name                  & File Dependency   & Location in Code \\
    \midrule
    \textbf{Section \rom{1}.A} \\
    \ \ \ Table 1                   & \bcode{Descriptive.R}      & \code{PK, PA} \\
    \textbf{Section \rom{1}.B} \\
    \ \ \ Figure 1                  & \bcode{Empirical\_AEJ.R}   & \code{PK}         & Section 1  \\
    \ \ \ Table 2                   & \bcode{Empirical\_AEJ.R}   & \code{PK}         & Section 2  \\
    \ \ \ Regression 1              & \bcode{Empirical\_AEJ.R}   & \code{PK}         & Section 1  \\
    \ \ \ Regressions 2, 3          & \bcode{Empirical\_AEJ.R}   & \code{PK}         & Section 2 \\
    \ \ \ Regression (!\#)          & \bcode{Empirical\_AEJ.R}   & \code{PK}         & Section 2 \\
    \textbf{Section \rom{1}.C} \\
    \ \ \ Figure 2                  & \bcode{Empirical\_AEJ.R}   & \code{CA, US}     & Section 3 \\
    \ \ \ Accounting                & \bcode{Accounting.R}       & \code{PK, CA, US} \\
    \textbf{Section \rom{2}.A} \\
    \ \ \ Figure 3                  & \bcode{Empirical\_AEJ.R}   & \code{CA}         & Section 4 \\
    \textbf{Section \rom{3}} \\
    \ \ \ Size Distribution         & \bcode{Empirical\_AEJ.R}   & \code{CA, US}     & Section 3 \\
    \ \ \ $\varphi_1$               & \bcode{Empirical\_AEJ.R}   & \code{CA} & Section 4 \\
    \ \ \ Clean share               & \bcode{Empirical\_AEJ.R}   & \code{PK} & Section 2 \\
    \ \ \ $k_E/Y$ for clean firms   & \bcode{Empirical\_AEJ.R}   & \code{PK} & Section 2 \\
    \ \ \ Figure 5                  & \bcode{twosectors.m}       & \multirow{2}{*}{\centering \code{*.mat}} \\
                                    & \bcode{plot\_figures.m} \\
    \textbf{Section \rom{4}.A} \\
    \ \ \ Table 4                   & \bcode{compute\_tables.m}  & \code{*.mat} \\
    \ \ \ Table 5                   & \bcode{compute\_tables.m}  & \code{*.mat} \\
    \ \ \ Figure 6                  & \bcode{plot\_figures.m}    & \code{*.mat} \\
    \ \ \ Decomposition             & \bcode{misc.m}             & \code{*.mat} \\
    \textbf{Section \rom{4}.B} \\
    \ \ \ Table 6                   & \bcode{compute\_tables.m}  & \code{*.mat} \\
    \ \ \ Decomposition             & \bcode{misc.m}             & \code{*.mat} \\
    \bottomrule
\end{tabular}
\label{tab:navi_main}
\begin{tablenotes}
     \footnotesize{
     \item[$\dagger$]
     Acronyms for datasets:
     \begin{itemize}[leftmargin=*]
        \item
        \bcode{KEYFIRM\_R.RData (PK)}: Key sources of the NGSPS.
        \item
        \bcode{ALLFIRM\_R.RData (PA)}: All sources of the NGSPS.
        \item
        \bcode{CNEC\_avgp.RData (CA)}: All samples in the CNEC.
        \item
        \bcode{susb04.csv (US)}: SUSB 2004.
     \end{itemize}
     }
     \item[$\ddag$]
     All the \code{*.mat} files will be produced by \bcode{twosectors.m}.
     \item[$\diamondsuit$]
     Notation (!\#) stands for ``un-numbered.''
\end{tablenotes}
\end{threeparttable}
\end{table}

\begin{enumerate}
    \item
    Table 1 is produced by the first part of \bcode{Descriptive.R}. All the numbers are printed to the terminal. Row 1 comes first, with Rows 2 and 3 follow.
    \item
    Regression (1) and Figure 1 are generated by Section 1 of \bcode{Empirical\_AEJ.R}. The regression results are printed to the terminal. Figure 1 is saved at \bcode{./Empirical/Results/Figure1.pdf}.
    \item
    Regressions (2), (3), and the un-numbered one in Section \rom{1}.B part \textit{The Role of End-of-pipe Treatment Technologies}, as well as Table 2 are produced by Section 2 of \bcode{Empirical\_AEJ.R}. As one exception, Section 2 relies on Section 1 of \bcode{Empirical\_AEJ.R}. The information in Table 2 is printed to the terminal in the order of Columns 2, 1, 3 and 4. The numbers in Columns 1 and 2 are directly taken from the output. Columns 3 and 4 are calculated by normalizing the physical equipment level to 100. Regression results are then printed to the terminal. First is the unnumbered regression, with those of Regressions (2) and (3) follow in order.
    \item
    Figure 2 is produced by Section 3 of \bcode{Empirical\_AEJ.R}. The two panels are exported as \\ \bcode{./Empirical/Results/Figure2\_Left.pdf} and \bcode{Figure2\_Right.pdf}.
    \item
    The in-text number of the accounting exercise can be calculated from the results following executing \bcode{Accounting.R}. The 33\% reduction in the last paragraph of Section \rom{1}.C part \textit{An Accounting Exercise} can then be calculated as the weighted average of the variable \bcode{ppar} with Row 1 of Table 1 as the weight. Notice that the variable \bcode{ppar} is exactly Row 3 of Table F.1. Because according to Row 1 of Table 1, the five industries combined contribute to 77\% of total COD emission, assuming that industries emitting the other 23\% COD remain intact, the 25\% reduction in average intensity is simply calculated as $1 - (67\% \times 77\% + 100\% \times 23\%) \triangleq 25\%$.
    \item
    Figure 3 is produced by the second part of Section 4 of \bcode{Empirical\_AEJ.R}. The two panels are exported as \bcode{./Empirical/Results/Figure3\_Left.pdf} and \bcode{Figure3\_Right.pdf}.
    \item
    To compute the quantitative results, the reader would need to execute \bcode{twosectors.m} several times. There are four cases to be computed: the benchmark case, the no distortion case, the regulation case and the flat tax case. The reader need to manually set the parameters in \bcode{twosectors.m} for each cases, namely the distortions \code{tauzd, tauzc}, the regulation intensity \code{xi} and the file name at the very end. The code is set to compute and save the benchmark results initially. The code contains all the relevant statements. The readers only need to comment and un-comment the relevant sections, which should be very easy to locate by searching for the variable name.
    \begin{enumerate}
        \item
        Execute \bcode{twosectors.m}. Some information would be printed to the terminal. Please refer to the log file \bcode{twosectors\_log.pdf} for details. The results are saved in \\ \bcode{./Quantitative/Results/benchmark\_new.mat}.
        \item
        Set \code{tauzd} and \code{tauzc} to zero, and the export destination to \bcode{./Results/notax\_new.mat}. The results will be saved in this file after execution. This case is labeled as Case (i) in the paper.
        \item
        Set \code{tauzd} and \code{tauzc} to the benchmark level, change \code{xi} to 0.355, and the export destination to \bcode{./Results/regulation\_new.mat}. The results will be saved in this file after execution. This case is labeled as Case (ii) in the paper.
        \item
        Set \code{tauzd} and \code{tauzc} to the flat tax level, reverse \code{xi} back to 0.23, and the export destination to \bcode{./Results/flattax\_new.mat}. The results will be saved in this file after execution. This case is labeled as Case (i') in the paper.
    \end{enumerate}
    \item
    With all the \code{*.mat} files computed, execute \bcode{plot\_figures.m} will produce Figures 5 and 6. The corresponding files will be saved under \bcode{./Quantitative/Results/}. The list of files include \\ \bcode{Figure5\_Left.pdf}, \bcode{Figure5\_Right.pdf}, \bcode{Figure6\_TopLeft.pdf}, \bcode{Figure6\_TopRight.pdf}, \\ \bcode{Figure6\_BotLeft.pdf} and \bcode{Figure6\_BotRight.pdf}.
    \item
    Tables 4, 5 and 6 are calculated using the output of \bcode{compute\_tables.m}. Notice that Tables 4 and 6 are presented in relative changes and share a similar structure. By changing the input files at the beginning of \bcode{compute\_tables.m} (in particular the 4 \code{.mat} just computed), \bcode{compute\_tables.m} prints the raw data of the corresponding entries in the same structure as the tables in the paper. Table 5 can be directly taken from the output \code{Table 5} of executing \bcode{compute\_tables.m} with the input being the corresponding cases. Entries in Table 4 can be calculated from the \code{Table 4} of the benchmark case and Cases (i) and (ii), while that of Table 6 can be calculated from \code{Table 4} of the benchmark case and Case (i'). The calculations of the relative changes are not automated, and the readers do have to do the calculations manually as we did. We apologize for the inconvenience. The in-text decomposition of the total reduction to the contribution of size distribution and technology adoption can be performed using \bcode{misc.m}. The readers need to change the second input file to either \bcode{notax\_new.mat} or \bcode{regulation\_new.mat}, depending on the cases to compute. The role of technology adoption is printed to the terminal, with the residual being that from the size distribution.
    \item
    Several calibration targets are computed from the data as well. This last bulletin explains where they are computed.
    \begin{itemize}
        \item
        The share of firms using clean technology 57\% is calculated in Section 2 of \bcode{Empirical\_AEJ.R}. The variable \code{clean\_share} hosts the number.
        \item
        The average adoption cost of clean technology as a ratio of output for clean firms 2.5\% is calculated at the end of Section 2 of \bcode{Empirical\_AEJ.R}. The number is printed to the terminal directly.
        \item
        The value of $\phi_1$ is computed in the first part of Section 4 of \bcode{Empirical\_AEJ.R}. The variable \code{phi\_quant} carries the information.
        \item
        The firm size and employment distributions [the light (yellow) bars in Figure 5] are computed at the end of Section 3 of \bcode{Empirical\_AEJ.R}. The variable \code{distchn} is first used to save the employment distribution and then the firm size distribution.
    \end{itemize}
\end{enumerate}

That concludes our instructions of replicating all the results in the main text.

\section{Replicate Results in the Appendices}

We now proceed with replicating the results in the appendices step-by-step. The results are presented in the order of appearance in the appendices. The correspondence between the results in the appendices and the section of code files is summarized in Table \ref{tab:navi_appendix}.

\begin{table}[t]
\footnotesize
\centering
\begin{threeparttable}
\caption{Navigating the Appendix}
\begin{tabular}{llll}
    \hline \hline
    Content                         & File Name                       & File Dependency          & Location in Code \\
    \midrule
    \textbf{Appendix A.1} \\
    \ \ \ Table A.1                 & \bcode{Descriptive.R}           & \code{PK, PA} \\
    \textbf{Appendix B} \\
    \ \ \ Figure B.1                & \bcode{Empirical\_Appendix.R}   & \code{PK, PA, DL, CA}    & Section 1  \\
    \textbf{Appendix C.1} \\
    \ \ \ Figure C.1                & \bcode{Empirical\_Appendix.R}   & \code{PK}                & Section 2  \\
    \ \ \ Table C.1                 & \bcode{Empirical\_Appendix.R}   & \code{PK}                & Section 2  \\
    \ \ \ Figure C.2                & \bcode{Empirical\_Appendix.R}   & \code{PK}                & Section 2  \\
    \ \ \ Regressions (!\#)         & \bcode{Empirical\_Appendix.R}   & \code{PK}                & Section 2  \\
    \ \ \ 3-Regressions (!\#)       & \bcode{Empirical\_AEJ.R}        & \code{PK}                & Section 2 \\
    \textbf{Appendix D.1} \\
    \ \ \ Figure D.1                & \bcode{Empirical\_Appendix.R}   & \code{CA}                & Section 4  \\
    \ \ \ Figure D.2                & \bcode{misc.m}       \\
    \textbf{Appendix D.2} \\
    \ \ \ Table D.1                 & \bcode{Empirical\_Appendix.R}   & \code{PK}                & Section 3  \\
    \ \ \ Regression (!\#)          & \bcode{Empirical\_Appendix.R}   & \code{PK}                & Section 3  \\
    \ \ \ Fixed Cost Ratio          & \bcode{Empirical\_Appendix.R}   & \code{PK}                & Section 3  \\
    \textbf{Appendix E.1} \\
    \ \ \ Figure E.1                & \bcode{Empirical\_Appendix.R}   & \code{CA, US}            & Section 5  \\
    \textbf{Appendix F} \\
    \ \ \ Table F.1                 & \bcode{Accounting.R}            & \code{PK, CA, US}  \\
    \textbf{Appendix J} \\
    \ \ \ Table J                   & \bcode{twosectors\_ces.m}       & \multirow{2}{*}{\centering \code{*.mat}} \\
                                    & \bcode{compute\_tables\_ces.m} \\
    \bottomrule
\end{tabular}
\label{tab:navi_appendix}
\begin{tablenotes}
     \footnotesize{
     \item[$\dagger$]
     Acronyms for datasets:
     \begin{itemize}[leftmargin=*]
        \item
        \bcode{KEYFIRM\_R.RData (PK)}: Key sources of the NGSPS.
        \item
        \bcode{ALLFIRM\_R.RData (PA)}: All sources of the NGSPS.
        \item
        \bcode{CNEC\_avgp.RData (CA)}: All samples in the CNEC.
        \item
        \bcode{DLARGE\_R.RData (DL)}: A subset of \code{CA} which overlaps with the 2004 Annual Surveys of Industrial Firm.
        \item
        \bcode{susb04.csv (US)}: SUSB 2004.
     \end{itemize}
     }
     \item[$\ddag$]
     All the \code{*.mat} files will be produced by \bcode{twosectors\_ces.m}.
     \item[$\diamondsuit$]
     Notation (!\#) stands for ``un-numbered.''     
\end{tablenotes}
\end{threeparttable}
\end{table}

\begin{enumerate}
    \item
    Table A.1 is produced by the second part of \bcode{Descriptive.R}. All numbers are printed to the terminal.
    \item
    Figure B.1 is generated by Section 1 of \bcode{Empirical\_Appendix.R}. The four panels are saved respectively as \bcode{./Empirical/Results/FigureB1\_TopLeft.pdf}, \bcode{FigureB1\_TopRight.pdf}, \\ \bcode{FigureB1\_BotLeft.pdf} and \bcode{FigureB1\_BotRight.pdf}.
    \item
    Section 2 of \bcode{Empirical\_Appendix.R} produces the results in Appendix C.1. The beginning of that section first runs the regression of intensity to size by industry. The regression results are printed to the terminal, which are exactly the results reported in Table C.1. The five panels of Figure C.1 are then exported to \bcode{./Empirical/Results/} with the names \bcode{FigureC1\_TopLeft.pdf}, \\ \bcode{FigureC1\_TopRight.pdf}, \bcode{FigureC1\_MidLeft.pdf}, \bcode{FigureC1\_MidRight.pdf} and \\ \bcode{FigureC1\_BotLeft.pdf}. Notice that the bottom-right panel is simply Figure 1 in the main text. The code then repeats the exercise for the manufacturing sector as a whole. Results to the un-numbered regressions on Pages 7, 9 and 10 (the last one) are then printed to the terminal, with Figure C.2 exported to \bcode{./Empirical/Results/FigureC2.pdf}.

    The three un-numbered regressions on the intensity-size relationship by the type of equipment are estimated in Section 2 of \bcode{Empirical\_AEJ.R}.
    \item
    The three panels of Figure D.1 are produced by Section 4 of \bcode{Empirical\_Appendix.R}. The figures are exported as \bcode{./Empirical/Results/FigureD1\_TopLeft.pdf}, \bcode{FigureD1\_TopRight} and \bcode{FigureD1\_Bot.pdf}.
    \item
    Figure D.2 is generated by the last part of \bcode{misc.m}. This requires the results from the benchmark case \bcode{./Quantitative/Results/benchmark\_new.mat}. The file hosts this figure would be \\ \bcode{./Quantitative/Results/FigureD2.eps}.
    \item
    Results in Appendix D.2 are computed by Section 3 of \bcode{Empirical\_Appendix.R}. Specifically, the 4 panels of Figures D.3 are first plotted and saved as \bcode{./Empirical/Results/FigureD3\_TopLeft.pdf}, \bcode{FigureD3\_TopRight.pdf}, \bcode{FigureD3\_BotLeft.pdf} and \bcode{FigureD3\_BotRight.pdf}. A series of results are then printed to the terminal: first are the in-text numbers of the mean of the ratio of adoption cost to output for firms with output in each quintile (22\%, 11\%, 6.7\%, 5.0\% and 2.7\%), second the coefficients of the un-numbered regression, with the results to Table D.3 come at last.
    \item
    Panels in Figure E.1 are produced by Section 5 of \bcode{Empirical\_Appendix.R}. The five panels are saved as \bcode{./Empirical/Results/FigureE1\_TopLeft.pdf}, \bcode{FigureE1\_TopRight.pdf}, \\ \bcode{FigureE1\_MidLeft.pdf}, \bcode{FigureE1\_MidRight.pdf} and \bcode{FigureE1\_BotLeft.pdf}. Similarly as for Figure C.1, the bottom-right panel is simply the left panel of Figure 2 in the main text.
    \item
    The accounting exercises in Appendix F are performed by \bcode{Accounting.R}. Variables \code{pmed}, \code{preg} and \code{ppar} are respectively for Rows 1, 2 and 3 in Table F.1.
    \item
    Finally, to reproduce Table J.1, one essentially follows the same logic as in the main text: namely execute \bcode{twosectors\_ces.m} many times with different parameter values, print the raw numbers for the corresponding variables and then manually compute the percentage changes in Table J.1. There are two cases in general, where CES $=$ 1.5 and CES $=$ 3.0. There are three parameters that are ``CES-specific:'' \code{sigmaces}, \code{ke} and \code{varces}. They are conveniently grouped together in the code, under the snippet \bcode{\% CES = 1.5} and  \bcode{\% CES = 3.0}. The readers would also need to modify \code{tauzd} and \code{tauzc} for different scenarios. As before, all the statements have been coded; and the readers only need to comment and un-comment the relevant snippets of the code. Likewise, the instruction to save the results at the end of the file also needs to be changed. One complication is that the readers need to set the initial guess for the market clearing prices. For each case, the initial guesses are conveniently stored in the code snippets at the beginning of Section \code{Solve the equilibrium wage}. The program is reasonable robust to different initial guesses. However, if the readers do not use the exact initial guess as we do, there may be very minor numerical difference for some of the variables. Similarly, if the reader uses other versions of MATLAB (we use 2016a) or Octave, such numerical errors would probably show up as well.
    \begin{enumerate}
        \item
        By default, \bcode{twosectors\_ces.m} is tuned to produce the benchmark results with CES $=$ 1.5. Executing the file would print some information to the terminal, again please refer to the log file \bcode{twosectors\_ces\_log.pdf} for detail. The equilibrium results are then saved under \\ \bcode{./Quantitative/Results/benchmark\_ces.mat}. This case is called benchmark.
        \item
        Set both \code{tauzd} to zero and leave \code{tauzc} untouched, change the initial guesses and the export destination. The results for eliminating only the distortions in the polluting sector would be saved under \bcode{./Quantitative/Results/nodirty\_ces.mat}. This is case (ii) in Appendix J.
        \item
        Set both \code{tauzd} and \code{tauzc} to zero, change the initial guesses and the export destination. The results for the no distortion case would be saved under \\ \bcode{./Quantitative/Results/notax\_ces.mat}. This case is labeled as case (i) in Appendix J.
    \end{enumerate}
    \item
    With all the \code{*.mat} files computed, as before, \bcode{compute\_tables\_ces.m} computes the raw data used in calculating entries in Table J.1. The results printed to the terminal can then be used to compute the percentage changes between equilibria in Table J.1. In particular, with the three cases at hand, the upper panel of Table J.1 can be reproduced.
    \item
    Repeat Steps 9 and 10 with the parameters set to CES $=$ 3.0 then produces the lower panel of Table J.1, which finally completes the replication of all the results in our paper.
\end{enumerate}
